Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-05-16 mu/article/article.tex
Correction of plot labels and eqns in text.

\subsection{Fixing spin}\label{sec:theory-fixspin}
Considering that we have 2D structures we can fix the spin direction along the
$x$, $y$, and $z$ Cartesian coordinates and then define the magnitude of the
spin velocity $|\mathcal{V}_{\sigma^{\mathrm{b}}}|$ in a fixed angle
$\gamma_{b}$ as
\begin{align}
|\mathcal{V}_{\sigma^{\mathrm{b}}}| (\omega)
&=
\sqrt{
(\mathcal{V}^{\mathrm{ax}}(\omega))^{2}\ +
(\mathcal{V}^{\mathrm{ay}}(\omega))^{2}\ 
}, 
\label{eq:vs-mag}
\\
\gamma_{\mathrm{b}} (\omega)
&=
\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega)}
{\mathcal{V}^{\mathrm{ax}}(\omega)} \right),
\label{eq:gamma-ang}
\end{align}
where the angle is measured in the counter-clockwise direction from the positive
$x$ axis.

@@

In a similar way we can fix the velocity in the $xy$ plane
along $x$ and $y$ directions and define $|\mathcal{V}^{\mathrm{a}}|$ as
\begin{equation}
|\mathcal{V}^{\mathrm{a}}| (\omega)= 
\sqrt {
(\mathcal{V}^{\mathrm{ax}}(\omega))^{2} +
(\mathcal{V}^{\mathrm{ay}}(\omega))^{2} +
(\mathcal{V}^{\mathrm{az}}(\omega))^{2} 
},
\label{eq:vv-mag}
\end{equation}
and the corresponding polar and azimuthal angles $\theta$ and $\varphi$ as
\begin{align}
\theta_{\mathrm{a}}  (\omega)
=& 
\cos^{-1} \left( \frac{\mathcal{V}^{\mathrm{az}}(\omega)}
{|\mathcal{V}^{\mathrm{a}}(\omega)|} \right),
& 0 \leq &\theta \leq \pi, 
\label{eq:polar-ang}
\\
\varphi_{\mathrm{a}} (\omega)
=& 
\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega)}
{\mathcal{V}^{\mathrm{ax}}(\omega)} \right),
& 0 \leq &\varphi \leq 2\pi.
\label{eq:azimuthal-ang} 
\end{align}

@@

We preset the results for $|\mathcal{V}^{\mathrm{a}}|(\omega)$ and
$|\mathcal{V}_{\sigma^{\mathrm{b}}}|(\omega)$ for the C$_{16}$H$_{8}$-alt and
C$_{16}$H$_{8}$-up structures being both noncentrosymmetric semi-infinite carbon
systems with 50\% hydrogenation in different arrangements. The \emph{alt} system
has alternating hydrogen atoms on the upper and bottom sides of the carbon
sheet, while the \emph{up} system has H only on the upper side. We take the
hexagonal carbon lattice to be on the $xy$ plane for both structures, and the
carbon-hydrogen bonds on the perpendicular $xz$ plane, as depicted in Figs.
\ref{fig:alt-struc} and \ref{fig:up-struc}.

Using the ABINIT code \cite{gonzeCPC09} we calculated the self-consistent ground
state and the Kohn-Sham states using density functional theory in the local
density approximation (DFT-LDA) with a planewave basis. We used Hartwigsen-
Goedecker-Hutter (HGH) relativistic separable dual-space Gaussian
pseudopotentials \cite{hartwigsenPRB98} including the spin-orbit interaction
needed to calculate $\mu^{\mathrm{abcd}}(\omega)$ (Eq.
\eqref{eq:mu}), $\mathcal{V}^{\mathrm{ab}}(\omega)$ (Eq. \eqref{eq:vab}),
$|\mathcal{V}_{\sigma^{\mathrm{b}}}|(\omega)$ (Eq. \eqref{eq:vs-mag}) and
$|\mathcal{V}^{\mathrm{a}}(\omega)|$ (Eq. \eqref{eq:vv-mag}).
%
It is known that using DFT-LDA to calculate the electronic structure of
materials predict a different band gap than the obtained experimentally. A
correction for the band gap energy value can be calculated by other 
\emph{ab-initio} methods such as the GW approximation \cite{onidaRMP02} but this
is outside the scope of this paper.
% 
The convergence parameters for the calculations of our results corresponding to
the \emph{alt} and \emph{up} structures are cutoff energies of 65\,Ha and
40\,Ha, respectively. The energy eigenvalues and matrix elements were calculated
using 14452 $\mathbf{k}$ points and 8452 $\mathbf{k}$ points in the irreducible
Brillouin zone (IBZ) and present LDA energy band gaps of 0.72\,eV and 0.088\,eV,
respectively for the \emph{alt} and \emph{up} structures.

@@

    \caption{Comparison of most intense responses of $\mathcal{V}^{\mathrm{ab}}$
    for \emph{alt}, \emph{up}, CdSe, and GaAs structures and the corresponding
    polarization angles.}
    \label{fig:vab-str-comp}
\end{figure}

@@

    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$, response
    vs. photon energy vs. polarization angle $\alpha$ for the \emph{up}
    structure for two energy ranges. The absolute maxima is located for an
    energy range from 0.08\,eV to 0.10\,eV and the local maximum from 1.95\,eV
    to 2.0\,eV and both for polarization angles between $25^{\circ}$ and
    $50^{\circ}$.}
    \label{fig:up-3d-vsz}
\end{figure}

@@

    \caption{Most intense response of
    $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ (top frames, right scale of
    figs (a) and (b)), the corresponding velocity angle
    $\gamma_{\mathrm{z}}(\omega)$ (top frames, right scale), the collinear
    (circled box) and perpendicular (square box) angles, and the two components
    $\mathcal{V}^{\mathrm{xz}}(\omega)$ and $\mathcal{V}^{\mathrm{yz}}(\omega)$
    (bottom frames) for the \emph{up} structure fixing the energy to 0.088\,eV.
    }
    \label{fig:up-vaz-rag}
\end{figure}

@@

where the absolute maximum of the $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$

@@

$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ spectra resulting from evaluate

@@

$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$, related to the left scale, fixing

@@

$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=95.8$\,Km/s coming from the

@@

$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=82.3$\,Km/s indicated by the upward

@@

value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=24.8$\,Km/s indicated by

@@

of $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=30.3$\,Km/s. This comes from a

@@

$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=23.5$\,Km/s indicated with the

@@

$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=9.0$\,Km/s indicated with the blue

@@

$|\mathcal{V}_{\sigma^{\mathrm{x}}}|(\omega)=37.4$\,Km/s and
$|\mathcal{V}_{\sigma^{\mathrm{y}}}|(\omega)=24.8$\,Km/s.

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-3d-svaz}
    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$, response
    vs. photon energy vs. polarization angle $\alpha$ for the \emph{alt}
    structure. The absolute maximum is located for an energy range from 0.90\,eV
    to 0.93\,eV and for polarization angles between $120^{\circ}$ and
    $150^{\circ}$.}
    \label{fig:alt-3d-vsb}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-vaz-rag}
    \caption{Most intense response of
    $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ (top frame, left scale) the
    corresponding velocity angle $\gamma_{\mathrm{z}}(\omega)$ (top frame, right
    scale), the collinear (circled box) and perpendicular (square box) angles,
    and the two components $\mathcal{V}^{\mathrm{xz}}(\omega)$ and
    $\mathcal{V}^{\mathrm{yz}}(\omega)$ (bottom frame) for the \emph{alt}
    structure fixing the energy to 0.912\,eV.}
    \label{fig:alt-vaz-rag}
\end{figure}

@@

For the \emph{alt} structure we analyzed the energy range for the incident beam from 0.6\,eV to 1.0\,eV, corresponding to the THz radiation, where the absolute maximum of $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ response is obtained.
% 
In Fig. \ref{fig:alt-3d-vsb} we present the
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$ spectra resulting from evaluate
again Eq. \eqref{eq:vs-mag} using different polarization angle $\alpha$ in Eq.
\eqref{eq:vab} for the \emph{alt} structure. In the figure we have that the
onset of the response starts when the energy of the incoming beam is the same of
the gap energy.
% 
From this figure we found that the zone where the absolute maximum response is
held corresponds to a energy range from 0.90\,eV to 0.93\,eV and polarization
angles $\alpha$ between $120^{\circ}$ and $150^{\circ}$. Also, a local maximum
is obtained for the same polarization angles but for energies between 0.67\,eV
and 0.75\,eV.
% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of ALT |V_{s^z}| & gamma  vs. alpha agle
% %%%%%%%%%%%%%%%%%
In the top frame of Fig. \ref{fig:alt-vaz-rag} we present in solid line the
result of evaluate $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)$, related to the
left scale, fixing the energy of the incoming beam to 0.912\,eV for which value
the response is maximized for the \emph{alt} structure. In the same figure and
frame we present with dashed line, related to the right scale, the velocity
angle $\gamma_{\mathrm{z}}(\omega)$ and in the bottom frame the corresponding
$\mathcal{V}^{\mathrm{xz}}(\omega)$ and $\mathcal{V}^{\mathrm{yz}}(\omega)$
components. Again, the circled and square boxes indicate the values for which
the polarization angle and the velocity angle are parallel and perpendicular and
with arrows are indicated the corresponding response value.
% 
From this figure and from Fig. \ref{fig:alt-3d-vsb} we have that the absolute
maximum response for the \emph{alt} structure is obtained for an incoming beam
with polarization angle $\alpha=145^{\circ}$ reaching a velocity of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=43.0$\,Km/s and for the spin
polarized in the $\mathrm{z}$ direction and resulting in a velocity angle
$\gamma_{\mathrm{z}}(\omega)=50^{\circ}$ on the first Cartesian Quadrant of the
$xy$ plane. The circled box for the collinear angle corresponds for angles
$\alpha$ and $\gamma_{\mathrm{z}}(\omega)$ equal to $53.5^{\circ}$ with a value
of $|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=12.7$\,Km/s, and the blue square
box indicates the perpendicular angles for values $\alpha=140^{\circ}$ and
$\gamma_{\mathrm{z}}(\omega)=50^{\circ}$ with a value of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}|(\omega)=43$\,Km/s. Finally we found that
for variations of $\pm0.5^{\circ}$ of those collinear and perpendicular angles,
presented with the error bars on the boxes, correspond ranges for the
polarization angle $30^{\circ} \leq \alpha \leq 70^{\circ}$ and $95^{\circ} \leq
\alpha \leq 175^{\circ}$ covering a wide range of angles because the response
angle $\gamma_{\mathrm{z}}(\omega)$ has small variations for the complete range
of the polarization angle $\alpha$.
% 
Again, for the cases in which the spin polarization is parallel to the surface
of the \emph{alt} structure was calculated but the plots are not presented here.
The absolute maxima for the case when the spin polarization is directed in the
$\mathrm{x}$ and $\mathrm{y}$ direction are obtained for an energy of the
incoming beam equal to 0.912\,eV and polarization angle $\alpha=145^{\circ}$
resulting in values of $|\mathcal{V}_{\sigma^{\mathrm{x}}}|(\omega)=27.1$\,Km/s
and $|\mathcal{V}_{\sigma^{\mathrm{y}}}|(\omega)=33.2$\,Km/s.

@@

\textbf{Up structure.}
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|(\omega)$ for \emph{up} structure
    \label{fig:up-3d-vvx-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-1}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|(\omega)$ for \emph{up} structure
    \label{fig:up-3d-vvy-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-1}}

    \caption{$|\mathcal{V}^{\mathrm{a}}|(\omega)$ response vs. photon energy vs.
    polarization angle for the \emph{up} structure. The absolute maxima of both
    responses $|\mathcal{V}^{\mathrm{x}}|(\omega)$ and
    $|\mathcal{V}^{\mathrm{y}}|(\omega)$ are localized in the energy
    range from 0.08\,eV to 0.10\,eV and for polarization angles from
    $25^{\circ}$ to $50^{\circ}$.}
    \label{fig:up-3d-vva-1}
\end{figure}
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|(\omega)$ 
    \label{fig:up-vx-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|(\omega)$ 
    \label{fig:up-vy-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}}

    \caption{Most intense response of
    $|\mathcal{V}^{\mathrm{x}}|(\omega)$ and
    $|\mathcal{V}^{\mathrm{y}}|(\omega)$ (top frames left scale of Figs. (a) and
    (b)), the corresponding polar $\varphi$ and azimuthal $\theta$ angles (top
    frames right scale), and the corresponding three components (bottom frames)
    for the \emph{up} structure fixing the polarization angle to
    $\alpha=40^{\circ}$ to maximize the response.}
    \label{fig:up-vab-comp-rtp-1}
\end{figure}

% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of UP |V^{a}| 3D
% %%%%%%%%%%%%%%%%%
For the \emph{up} structure we first analyzed the energy range from 0.00\,eV to
0.16\,eV, where we found the most intense response and the absolute maxima for
$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$
presented in Fig. \ref{fig:up-3d-vva-1} and resulting from evaluate Eq.
\eqref{eq:vv-mag} using different polarization angles $\alpha$ in Eq.
\eqref{eq:vab} for the \emph{up} structure. We can see that the onset of the
response is when the energy of the incoming light is the same of the gap energy.
%
From this picture we can see that for the zone between the energy range of
0.084\,eV-0.093\,eV and polarization angles between $30^{\circ}$ and
$45^{\circ}$ is the zone where the maximum response is held for both,
$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$.
% %%%%%%%%%%%%%%%%%
% %% 1.8 eV - 2.0 eV
% %% Description of UP |V^{a}|, components and RTP
% %%%%%%%%%%%%%%%%%

In the top frames of  Figs. \ref{fig:up-vx-comp-rtp-1} and 
% 
\ref{fig:up-vy-comp-rtp-1} we present in solid lines the results of
$|\mathcal{V}^{\mathrm{x}}|(\omega)$ and $|\mathcal{V}^{\mathrm{y}}|(\omega)$,
related to the left scale, fixing the polarization angle to $\alpha=40^{\circ}$
for which the response is maximized. In the same
figures and frames we present in dashed lines the corresponding polar
$\theta_{a}(\omega)$ and azimuthal $\varphi_{a}(\omega)$ angles related to the
right scale. Also, in the bottom frames of those figures we present the
decomposition of $|\mathcal{V}^{\mathrm{x}}|(\omega)$ and
$|\mathcal{V}^{\mathrm{y}}|(\omega)$ in the corresponding
$\mathcal{V}^{\mathrm{xx}}(\omega)$, $\mathcal{V}^{\mathrm{xy}}(\omega)$,
$\mathcal{V}^{\mathrm{xz}}(\omega)$, and $\mathcal{V}^{\mathrm{yx}}(\omega)$,
$\mathcal{V}^{\mathrm{yy}}(\omega)$, $\mathcal{V}^{\mathrm{yz}}(\omega)$
components.
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vvx-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ for \emph{up} structure 
    \label{fig:up-3d-vvy-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}}

>>>>

\subsection{Fixing spin}\label{sec:theory-fixspin}
Considering that we have 2D structures we can fix the spin direction along the
$x$, $y$, and $z$ Cartesian coordinates and then define the magnitude of the
spin velocity $|\mathcal{V}_{\sigma^{\mathrm{b}}}|$ in a fixed angle
$\gamma_{b}$ as
\begin{align}
|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega)| 
&=
\sqrt{
[\mathcal{V}^{\mathrm{ax}}(\omega)]^{2}\ +
[\mathcal{V}^{\mathrm{ay}}(\omega)]^{2}\ 
}, 
\label{eq:vs-mag}
\\
\gamma_{\mathrm{b}} (\omega)
&=
\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega)}
{\mathcal{V}^{\mathrm{ax}}(\omega)} \right),
\label{eq:gamma-ang}
\end{align}
where the angle is measured in the counter-clockwise direction from the positive
$x$ axis.

@@

In a similar way we can fix the velocity in the $xy$ plane
along $x$ and $y$ directions and define $|\mathcal{V}^{\mathrm{a}}|$ as
\begin{equation}
|\mathcal{V}^{\mathrm{a}}(\omega)| = 
\sqrt {
[\mathcal{V}^{\mathrm{ax}}(\omega)]^{2} +
[\mathcal{V}^{\mathrm{ay}}(\omega)]^{2} +
[\mathcal{V}^{\mathrm{az}}(\omega)]^{2} 
},
\label{eq:vv-mag}
\end{equation}
and the corresponding polar and azimuthal angles $\theta$ and $\varphi$ as
\begin{align}
\theta_{\mathrm{a}}  (\omega)
=& 
\cos^{-1} \left( \frac{\mathcal{V}^{\mathrm{az}}(\omega)}
{|\mathcal{V}^{\mathrm{a}}(\omega)|} \right),
& 0 \leq &\theta \leq \pi, 
\label{eq:polar-ang}
\\
\varphi_{\mathrm{a}} (\omega)
=& 
\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega)}
{\mathcal{V}^{\mathrm{ax}}(\omega)} \right),
& 0 \leq &\varphi \leq 2\pi.
\label{eq:azimuthal-ang} 
\end{align}

@@

We preset the results for $|\mathcal{V}^{\mathrm{a}}(\omega)|$ and
$|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega)|$ for the C$_{16}$H$_{8}$-alt and
C$_{16}$H$_{8}$-up structures being both noncentrosymmetric semi-infinite 2D
carbon systems with 50\% hydrogenation in different arrangements. The \emph{alt}
system has alternating hydrogen atoms on the upper and bottom sides of the
carbon sheet, while the \emph{up} system has H only on the upper side. We take
the hexagonal carbon lattice to be on the $xy$ plane for both structures, and
the carbon-hydrogen bonds on the perpendicular $xz$ plane, as depicted in Figs.
\ref{fig:alt-struc} and \ref{fig:up-struc}.

Using the ABINIT code \cite{gonzeCPC09} we calculated the self-consistent ground
state and the Kohn-Sham states using density functional theory in the local
density approximation (DFT-LDA) with a planewave basis. We used Hartwigsen-
Goedecker-Hutter (HGH) relativistic separable dual-space Gaussian
pseudopotentials \cite{hartwigsenPRB98} including the spin-orbit interaction
needed to calculate $\mu^{\mathrm{abcd}}(\omega)$ presented in Eq.
\eqref{eq:mu}.
% 
It is known that using DFT-LDA to calculate the electronic structure of
materials predict a different band gap than the obtained experimentally. A
correction for the band gap energy value can be calculated by other 
\emph{ab-initio} methods such as the GW approximation \cite{onidaRMP02} but this
is outside the scope of this paper.
% 
The convergence parameters for the calculations of our results corresponding to
the \emph{alt} and \emph{up} structures are cutoff energies of 65\,Ha and
40\,Ha, respectively. The energy eigenvalues and matrix elements were calculated
using 14452 $\mathbf{k}$ points and 8452 $\mathbf{k}$ points in the irreducible
Brillouin zone (IBZ) and present LDA energy band gaps of 0.72\,eV and 0.088\,eV,
respectively for the \emph{alt} and \emph{up} structures.

@@

    \caption{Comparison of most intense responses of $\mathcal{V}^{\mathrm{ab}}$
    for 2D \emph{alt} and \emph{up}, and bulk CdSe and GaAs structures and the
    corresponding polarization angles.}
    \label{fig:vab-str-comp}
\end{figure}

@@

    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$, response
    vs. photon energy vs. polarization angle $\alpha$ for the \emph{up}
    structure for two energy ranges. The absolute maxima is located for an
    energy range from 0.08\,eV to 0.10\,eV and the local maximum from 1.95\,eV
    to 2.0\,eV and both for polarization angles between $25^{\circ}$ and
    $50^{\circ}$.}
    \label{fig:up-3d-vsz}   
\end{figure}

@@

    \caption{Most intense response of
    $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$ (top frames, right scale of
    figs (a) and (b)), the corresponding velocity angle
    $\gamma_{\mathrm{z}}(\omega)$ (top frames, right scale), the collinear
    (circled box) and perpendicular (square box) angles, and the two components
    $\mathcal{V}^{\mathrm{xz}}(\omega)$ and $\mathcal{V}^{\mathrm{yz}}(\omega)$
    (bottom frames) for the \emph{up} structure fixing the energy to 0.088\,eV.
    }
    \label{fig:up-vaz-rag}
\end{figure}

@@

where the absolute maximum of the $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$

@@

$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$ spectra resulting from evaluate

@@

$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$, related to the left scale, fixing

@@

$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=95.8$\,Km/s coming from the

@@

$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=82.3$\,Km/s indicated by the upward

@@

value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=24.8$\,Km/s indicated by

@@

of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=30.3$\,Km/s. This comes from a

@@

$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=23.5$\,Km/s indicated with the

@@

$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=9.0$\,Km/s indicated with the blue

@@

$|\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega)|=37.4$\,Km/s and
$|\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega)|=24.8$\,Km/s.

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-3d-svaz}
    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$, response
    vs. photon energy vs. polarization angle $\alpha$ for the \emph{alt}
    structure. The absolute maximum is located for an energy range from 0.90\,eV
    to 0.93\,eV and for polarization angles between $120^{\circ}$ and
    $150^{\circ}$.}
    \label{fig:alt-3d-vsb}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-vaz-rag}
    \caption{Most intense response of
    $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$ (top frame, left scale) the
    corresponding velocity angle $\gamma_{\mathrm{z}}(\omega)$ (top frame, right
    scale), the collinear (circled box) and perpendicular (square box) angles,
    and the two components $\mathcal{V}^{\mathrm{xz}}(\omega)$ and
    $\mathcal{V}^{\mathrm{yz}}(\omega)$ (bottom frame) for the \emph{alt}
    structure fixing the energy to 0.912\,eV.}
    \label{fig:alt-vaz-rag}
\end{figure}

@@

For the \emph{alt} structure we analyzed the energy range for the incident beam
from 0.6\,eV to 1.0\,eV, corresponding to the THz radiation, where the absolute
maximum of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$ response is obtained.
% 
In Fig. \ref{fig:alt-3d-vsb} we present the
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$ spectra resulting from evaluate
again Eq. \eqref{eq:vs-mag} using different polarization angle $\alpha$ in Eq.
\eqref{eq:vab} for the \emph{alt} structure.
% 
From this figure we found that the zone where the absolute maximum response is
held corresponds to a energy range from 0.90\,eV to 0.93\,eV and polarization
angles $\alpha$ between $120^{\circ}$ and $150^{\circ}$. Also, a local maximum
is obtained for the same polarization angles but for energies between 0.67\,eV
and 0.75\,eV.
% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of ALT |V_{s^z}| & gamma  vs. alpha agle
% %%%%%%%%%%%%%%%%%
In the top frame of Fig. \ref{fig:alt-vaz-rag} we present in solid line the
result of evaluate $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$, related to the
left scale, fixing the energy of the incoming beam to 0.912\,eV for which value
the response is maximized for the \emph{alt} structure. In the same figure and
frame we present with dashed line, related to the right scale, the velocity
angle $\gamma_{\mathrm{z}}(\omega)$ and in the bottom frame the corresponding
$\mathcal{V}^{\mathrm{xz}}(\omega)$ and $\mathcal{V}^{\mathrm{yz}}(\omega)$
components. Again, the circled and square boxes indicate the values for which
the polarization angle and the velocity angle are parallel and perpendicular and
with arrows are indicated the corresponding response value.
% 
From this figure and from Fig. \ref{fig:alt-3d-vsb} we have that the absolute
maximum response for the \emph{alt} structure is obtained for an incoming beam
with polarization angle $\alpha=145^{\circ}$ reaching a velocity of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=43.0$\,Km/s and for the spin
polarized in the $\mathrm{z}$ direction and resulting in a velocity angle
$\gamma_{\mathrm{z}}(\omega)=50^{\circ}$ on the first Cartesian Quadrant of the
$xy$ plane. The circled box for the collinear angle corresponds for angles
$\alpha$ and $\gamma_{\mathrm{z}}(\omega)$ equal to $53.5^{\circ}$ with a value
of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=12.7$\,Km/s, and the blue square
box indicates the perpendicular angles for values $\alpha=140^{\circ}$ and
$\gamma_{\mathrm{z}}(\omega)=50^{\circ}$ with a value of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=43$\,Km/s. Finally we found that
for variations of $\pm0.5^{\circ}$ of those collinear and perpendicular angles,
presented with the error bars on the boxes, correspond ranges for the
polarization angle $30^{\circ} \leq \alpha \leq 70^{\circ}$ and $95^{\circ} \leq
\alpha \leq 175^{\circ}$ covering a wide range of angles because the response
angle $\gamma_{\mathrm{z}}(\omega)$ has small variations for the complete range
of the polarization angle $\alpha$.
% 
Again, for the cases in which the spin polarization is parallel to the surface
of the \emph{alt} structure was calculated but the plots are not presented here.
The absolute maxima for the case when the spin polarization is directed in the
$\mathrm{x}$ and $\mathrm{y}$ direction are obtained for an energy of the
incoming beam equal to 0.912\,eV and polarization angle $\alpha=145^{\circ}$
resulting in values of $|\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega)|=27.1$\,Km/s
and $|\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega)|=33.2$\,Km/s.

@@

\textbf{Up structure.}
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}(\omega)|$ for \emph{up} structure
    \label{fig:up-3d-vvx-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-1}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}(\omega)|$ for \emph{up} structure
    \label{fig:up-3d-vvy-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-1}}

    \caption{$|\mathcal{V}^{\mathrm{a}}(\omega)|$ response vs. photon energy vs.
    polarization angle for the \emph{up} structure. The absolute maxima of both
    responses $|\mathcal{V}^{\mathrm{x}}(\omega)|$ and
    $|\mathcal{V}^{\mathrm{y}}(\omega)|$ are localized in the energy
    range from 0.08\,eV to 0.10\,eV and for polarization angles from
    $25^{\circ}$ to $50^{\circ}$.}
    \label{fig:up-3d-vva-1}
\end{figure}
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}(\omega)|$ 
    \label{fig:up-vx-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}(\omega)|$ 
    \label{fig:up-vy-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}}

    \caption{Most intense response of
    $|\mathcal{V}^{\mathrm{x}}(\omega)|$ and
    $|\mathcal{V}^{\mathrm{y}}(\omega)|$ (top frames left scale of Figs. (a) and
    (b)), the corresponding polar $\varphi$ and azimuthal $\theta$ angles (top
    frames right scale), and the corresponding three components (bottom frames)
    for the \emph{up} structure fixing the polarization angle to
    $\alpha=40^{\circ}$ to maximize the response.}
    \label{fig:up-vab-comp-rtp-1}
\end{figure}

% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of UP |V^{a}| 3D
% %%%%%%%%%%%%%%%%%
For the \emph{up} structure we first analyzed the energy range from 0.00\,eV to
0.16\,eV, where we found the most intense response and the absolute maxima for
$|\mathcal{V}^{\mathrm{x}}(\omega)|$ and $|\mathcal{V}^{\mathrm{y}}(\omega)|$
presented in Fig. \ref{fig:up-3d-vva-1} and resulting from evaluate Eq.
\eqref{eq:vv-mag} using different polarization angles $\alpha$ in Eq.
\eqref{eq:vab} for the \emph{up} structure.
%
From this picture we can see that for the zone between the energy range of
0.084\,eV-0.093\,eV and polarization angles between $30^{\circ}$ and
$45^{\circ}$ is the zone where the maximum response is held for both,
$|\mathcal{V}^{\mathrm{x}}(\omega)|$ and $|\mathcal{V}^{\mathrm{y}}(\omega)|$.
% %%%%%%%%%%%%%%%%%
% %% 1.8 eV - 2.0 eV
% %% Description of UP |V^{a}|, components and RTP
% %%%%%%%%%%%%%%%%%

In the top frames of  Figs. \ref{fig:up-vx-comp-rtp-1} and 
% 
\ref{fig:up-vy-comp-rtp-1} we present in solid lines the results of
$|\mathcal{V}^{\mathrm{x}}(\omega)|$ and $|\mathcal{V}^{\mathrm{y}}(\omega)|$,
related to the left scale, fixing the polarization angle to $\alpha=40^{\circ}$
for which the response is maximized. In the same
figures and frames we present in dashed lines the corresponding polar
$\theta_{a}(\omega)$ and azimuthal $\varphi_{a}(\omega)$ angles related to the
right scale. Also, in the bottom frames of those figures we present the
decomposition of $|\mathcal{V}^{\mathrm{x}}(\omega)|$ and
$|\mathcal{V}^{\mathrm{y}}(\omega)|$ in the corresponding
$\mathcal{V}^{\mathrm{xx}}(\omega)$, $\mathcal{V}^{\mathrm{xy}}(\omega)$,
$\mathcal{V}^{\mathrm{xz}}(\omega)$, and $\mathcal{V}^{\mathrm{yx}}(\omega)$,
$\mathcal{V}^{\mathrm{yy}}(\omega)$, $\mathcal{V}^{\mathrm{yz}}(\omega)$
components.
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vvx-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ for \emph{up} structure 
    \label{fig:up-3d-vvy-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}}
